### 2023-10-23 results/celegans.tex
Going home, headache ...

>>>>

The digital results of the \ac{C. elegans} dataset are quite numerous, not all of them can be displayed and analyzed. For this reason, only a selected four sequences will be displayed as the results of the dataset are not the focus of this thesis. The full work around the \ac{C. elegans} dataset and problem is done in \cite{celegans}.

\begin{figure}[H]
  \centering
  \begin{minipage}{\columnwidth}
    \subfloat[Analog prediction for the DB1 neuron\label{graph:digital5BD1Celegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/digital5DB1}}%
    \hfill
    \subfloat[Analog prediction for the LUAL neuron\label{graph:digital5LUALCelegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/digital5LUAL}}%
  \end{minipage}
  \begin{minipage}{\columnwidth}
    \subfloat[Analog prediction for the PVR neuron\label{graph:digital5PVRCelegans}]{\includesvg[width=0.5\textwidth, pretex=\tiny]{results/celegans/digital5PVR}}%
    \hfill
    \subfloat[Analog prediction for the VB1 neuron\label{graph:digital5VB1Celegans}]{\includesvg[width=0.5\textwidth,pretex=\tiny]{results/celegans/digital5VB1}}%
  \end{minipage}
  \caption{\ac{C. elegans} digital responses with their digital counterparts spread out for each output neuron}
  \label{graph:spread5Celegans}
\end{figure}
